---
title       : Developing Data Products
subtitle    : shiny & slidify at work
author      : Shawn Tan
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [rCharts]            # {mathjax, quiz, bootstrap}
ext_widgets  : {rCharts: [libraries/nvd3]}
mode        : selfcontained # {standalone, draft}
---

## Background & Features

<ol>
<li> An app is written using the shiny package in R.</li>
<li> The app serves to provide a visual understanding of the mtcars dataset.</li>
<li> Several different forms of visual representation are provided, including: </li>
<ul>
<li>  A visual correlation matrix of all variables in the dataset,</li>
<li>  visualization of the effect of a single variable across all car types,</li>
<li>  visualization of how two selected variables are correlated</li>
</ul>
<li> The app also provides linear regression models between two variables. </li>
</ol>

--- .class #id 

## Visual Representation of Data - Overview

A correlation matrix is provided to give an overview of variables in the dataset.

```{r echo=F, message=FALSE, results='asis'}
corrplot(cor(mtcars),type="lower")
title("Multivariable Correlation",line=-1)
```

---

## Visual Representation of Data - Impact of Variables

Several different types of visualization are available in this shiny app, allowing the user to see a single variable across car types and the correlation between two variables.

```{r echo=F, fig.width=13, fig.height=7, message=FALSE, results='asis'}
library(datasets)
par(mfcol=c(1,2))
dotchart(mtcars$mpg,labels=row.names(mtcars),cex=1,col=36,pch=19,
      xlab="Mileage",main="Single Variable Across Car Types")
plot(mtcars$mpg,mtcars$wt,
         xlab="Mileage",ylab="Weight",pch=19,col=35,cex=1.5,main="Two-Variable Analaysis")

```

---

## Source Codes and Supplementary Information

The source code for this project can be found at the following links:

- Github repository: https://github.com/xtrios/DDP
- Shiny app for mtcars visualization: http://xtrios.shinyapps.io/DDP-mtcars
- Location of Slidify deck: http://xtrios.github.io/slidify-deck/

Try out the app now at: https://github.com/xtrios/DDP!


